---
title: "Homework 9"
author: "Kimberly McNeil"
date: "4/2/2026"
output:
  html_document:
    code_folding: show
linkcolor: blue
urlcolor: blue
---

```{r setup, include=FALSE, echo=TRUE}
# remember warning=FALSE and message=FALSE only when done
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(babynames)
library(dplyr)
```

```{r}
View(babynames)
```


## Proportion Percentages

The following table showcases the first 6 rows of babynames with a new column that converts the prop column into percentages, rounded to two decimal places:^[Question 1 Complete]

```{r}
babynames_percent = babynames %>%
  mutate(percent = round(prop * 100, 2))

babynames_percent %>%
  head() %>%
  kable()
```



## Percentages per year

The following table showcases the first 6 rows of the previous table with a new column that customizes the following string template: “PERCENT% in YEAR”:^[Question 2 Complete]

```{r}
babynames_str = babynames_percent %>%
  mutate(percent_year = str_glue("{percent}% in {year}"))

babynames_str %>%
  head() %>%
  kable()
```


## Custom Name and Sex




## Sampling Five Rows




## Flatten Strings




## Final Results