---
title: "Homework 9"
author: "Kimberly McNeil"
date: "4/2/2026"
output:
  html_document:
    code_folding: show
linkcolor: blue
urlcolor: blue
---

```{r setup, include=FALSE, echo=TRUE, warning=FALSE, message=FALSE}
# remember warning=FALSE and message=FALSE only when done
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(babynames)
library(dplyr)
```

## Proportion Percentages

The following table showcases the first 6 rows of babynames with a new column that converts the prop column into percentages, rounded to two decimal places:^[Question 1 Complete]

```{r}
babynames_percent = babynames %>%
  mutate(percent = round(prop * 100, 2))

babynames_percent %>%
  head() %>%
  kable()
```


## Percentages per Year

The following table showcases the first 6 rows of the previous table with a new column that customizes the following string template: “PERCENT% in YEAR”:^[Question 2 Complete]

```{r}
babynames_str = babynames_percent %>%
  mutate(percent_year = str_glue("{percent}% in {year}"))

babynames_str %>%
  head() %>%
  kable()
```


## Custom Name and Sex

The following table showcases the first 6 rows of the previous table filtered for those with the name "Kimberly" with a Sex of "F":^[Question 3 Complete]

```{r}
name_filter = babynames_str %>%
  filter(name == "Kimberly", sex == "F")

name_filter %>%
  head() %>%
  kable()
```


## Sampling Five Rows

The following table showcases five randomly selected observations, sorted chronologically:^[Question 4 Complete]

```{r}
set.seed(42)

sampled_data = name_filter %>%
  slice_sample(n = 5) %>%
  arrange(year)

sampled_data %>%
  kable()
```


## Flatten Strings

The following string showcases the previous five random rows' "percentage in year" strings from the Percentages per Year section flattened into a single string:^[Question 5 Complete]

```{r}
string_vector = sampled_data %>%
  pull(percent_year)

flattened_string = str_flatten(string_vector, ", ", last = ", and ")

str_view(flattened_string)
```


## Final Results

```{r results = 'asis'}
final_results = str_glue("Out of all Female names, the name Kimberly represented {flattened_string}.")

cat(final_results)
```
^[Question 6 Complete]